---
title: "Exercise Manner Prediction"
author: "Bai"
date: "Tuesday, August 18, 2015"
output: 
  html_document:
    keep_md: true
---

##Synopsis
The goal of this project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set.

##Data Processing
Download training data and testing data. 
```{r,echo=TRUE,cache=TRUE}
# read file into data frame
trainingDF <- read.csv("./data/pml-training.csv",na.strings = c('NA','#DIV/0!',''))
testingDF  <- read.csv("./data/pml-testing.csv",na.strings = c('NA','#DIV/0!',''))
```
Split the training data into training set to build the prediction model (70%) and testing set for model validation (30%).
```{r,echo=TRUE,cache=TRUE,warning=FALSE}
library(caret)
set.seed(32323)
inTrain <- createDataPartition(y=trainingDF$classe,p=.7,list=FALSE)
training <- trainingDF[inTrain,]
testing  <- trainingDF[-inTrain,]
dim(training);dim(testing)
```

##Data Exploratory and Cleaning
All the data exploratory is applied on the training set.Note there are 159 variables in the dataset. Let's check the NAs in each column and clean the variables with NAs. 

```{r,echo=TRUE,cache=TRUE}
feature_index <- colnames(training)
feature_index <- colnames(training[colSums(is.na(training)) == 0])
length(feature_index)
```
There are 60 columns without NAs. By observating those columns, remove column 1 to 7 which are discriptions of the record.

```{r,echo=TRUE,cache=TRUE}
feature_index
feature_index <- feature_index[-c(1:7)]
training <- training[,feature_index]
dim(training)
```

##Preprocess and Model 
Use PCA method in preprocess and rf as prediction model.

```{r,echo=TRUE,cache=TRUE,warning=FALSE}

modelFit <- train(training$classe ~ .,method="rf",preProcess="pca",data=training[,-53],na.action=na.pass)
modelFit
```

##Cross Validation
Apply the model on testing set and compare with the real result. The Accuracy is 97.16%. The out of sample error is 1-accuracy which is 0.0284.

```{r,echo=TRUE,cache=TRUE,warning=FALSE}
confusionMatrix(testing$cla,predict(modelFit,testing[,-53]))
```

##Prediction
Apply the model on the test file.
```{r,echo=TRUE,cache=TRUE}
predict(modelFit,testingDF)
```


